Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-09 krs-survey.tex
Enriched section on knowledge instantiation

Cognitive architectures and KRS in particular are consequently often
benchmarked with synthetic datasets (which leads to other issues: how to assess
the meaningfulness of the performance of a reasoner on an artificial
ontology?~\cite{Bail2010}) or \emph{toy} experiments~\cite{Chong2009} that do
not reflect real-world complexity.

While evaluating the performances of knowledge representation systems
themselves may be difficult, the cognitive performances of the robot as a whole
can be aptly evaluated through ``classical'' tests from the psychology (like
False-Belief experiments~\cite{Leslie2000} or the Token
test~\cite{DiSimoni1978}).

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.2} Alignement with Standards}}
            child {node {{\bf F.1} Self-Knowledge}}
 \end{tikzpicture}
\end{center}
\end{scriptsize}

How much knowledge is available? Which content? How big is the knowledge base?

\begin{itemize}
	\item  Which underlying knowledge (\emph{common-sense}, \emph{upper knowledge}\ldots{})
	\begin{itemize}
		\item  top-down approach?
	\end{itemize}

@@

\subsubsection{Alignment with Standard Upper-Ontologies}

@@

>>>>

Cognitive architectures and KRS in particular are consequently often
benchmarked with synthetic datasets (which leads to other issues: how to assess
the meaningfulness of the performance of a reasoner on an artificial
ontology?~\cite{Bail2010}) or toy experiments~\cite{Chong2009} that do
not reflect real-world complexity.

While evaluating the performances of knowledge representation systems
themselves may be difficult, the cognitive performances of the robot as a whole
can be also evaluated through ``classical'' tests from the psychology (like
False-Belief experiments~\cite{Leslie2000} or the Token
test~\cite{DiSimoni1978}).

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.4} Alignement with Standards}}
            child {node {{\bf F.3} Self-Knowledge}}
            child {node {{\bf F.2} Metrics}}
            child {node {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

\subsubsection{Design Strategy}

Ontology engineering has grown into a research field of its own\fxwarning{Give
some idea about it? wikipedia?}.

Two main approaches are common in the cognitive robotic community:
\emph{top-down} design and \emph{bottom-up}.

Several strategies ... Designing, implementing and feeding an ontological model of the beliefs of the robot

\begin{itemize}
    \item Dynamic, run-time instantiation
    \item Static, a priori knowledge
    \item Fetch from external resources (TBox and/or ABox)
\end{itemize}

\subsubsection{Metrics}

Qualitative and quantitative metrics give an oversight of the size and
expressive complexity of ontologies.

Table~\ref{table|upper_onto_metrics} gives such metrics for four major
upper-ontologies commonly used in the semantic Web community.

\fxwarning{Add metrics for SUMO, OpenCyc, ResearchCyc}

\begin{table}
\begin{center}

\begin{tabular}{llllll}
\toprule
{\bf Project} & {\bf Expressiveness} & {\bf Axioms} & {\bf Classes} & {\bf Properties} & {\bf Instances} \\
\midrule
OpenCyc \\
ResearchCyc \\
SUMO \\
DBPedia \\
\bottomrule

\end{tabular}
\end{center}
\caption{Selection of metrics for the major upper-ontologies.}
\label{table|upper_onto_metrics}
\end{table}

@@

\subsubsection{Alignment with Standard Upper-ontologies}

@@

\subsubsection{Assessing performances}

The systems we have presented share the property to have real implementations
on real, physical robots. This simple fact allows to first assert that these
tools are at least viable solutions to the question: how to endow a (real)
robot with explicit knowledge manipulation capabilities?

From a theoritical point of view, this work hopefully brings elements of
comparison and evaluation of the existing systems.

However, this do not suffice to assess and comment the suitability of such
systems to real-world tasks. As hinted in section~\ref{sect|performances}, we
think that first, the practical evaluation of knowledge representation systems
for robots can not take place in isolation (links with perceptual and
decisional layers are too important), then we should evaluate the robot
behaviour at the scale of the whole system, basing experiments on established
protocols, borrowed from other disciplines from cognitive sciences. We have
already mentioned classical experiments like False-Beliefs in psychology or the
Token test in linguistic. A systematic review of standard cognitive tests
applicable to service robots is still to be made.
